Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features

### 2016-12-20 paper/structureScene.tex
Shorten intro slightly

The next question is the choice of a classifier. Here, a class of particularly successful algorithms train a classifier, such as a support vector machine (SVM) \cite{cristianini2000introduction}, to discriminate between short extracts of an auditory scene, and at the classification stage divide the signal into short extracts which are classified separately before pooling the classification results to reach a final decision. This last step is known as late integration and is crucial to the success of these methods, since it allows the classifier to concentrate on the short, distinct sound events that discriminate between scenes. The success of the late integration technique again leads credence to the idea that rare, distinct events in an auditory scene are sufficient to characterize it almost completely. Combining scattering transforms for low-level representation with late-integrated SVMs used for classifying the scene at a higher level, we obtain a competitive auditory scene classification system, demonstrating the usefulness of both concepts for this task.

>>>>

The next question is the choice of a classifier. Here, a class of particularly successful algorithms train a classifier, such as a support vector machine (SVM) \cite{cristianini2000introduction}, to discriminate between short extracts of an auditory scene, and at the classification stage divide the signal into short extracts which are classified separately before pooling the classification results to reach a final decision. This last step is known as late integration and is crucial to the success of these methods, since it allows the classifier to concentrate on the short, distinct sound events that discriminate between scenes. The success of the late integration technique again leads credence to the idea that rare, distinct events in an auditory scene are sufficient to characterize it almost completely. Combining scattering transforms for low-level representation with late-integrated SVMs for classifying the scene at a higher level, we obtain a competitive auditory scene classification system, demonstrating the usefulness of both concepts for this task.
